### 2020-12-31 treatise-pdflatex/abstract.tex
Create pdflatex version

Multiple-input-multiple-output (MIMO) is the future of wireless communication, but the large number of antennae makes it difficult to estimate its channel state information.
Since millimeter wave (mm-Wave) band, often used together with MIMO, is known to exhibit sparsity, results on compressive sensing suggest that, on mm-Wave band, fewer channel measurements shall suffice.
Current literature prefers orthogonal matching pursuit (OMP) due to its lower complexity.
It is interesting to note that Dantzig Selector (DS), claimed to have various performance guarantee, has seldom been examined.

In this treatise, we consider a mm-Wave MIMO channel, and a hybrid structure at both the transmitter and receiver end.
Using pilot signal and 
We demonstrate that DS can be applied on a entrywise i.i.d.\ random beamformer, and give a bound for its expected error norm, which holds for high probability.
DS is cast as a linear program, and simulation is done.
We argue that DS is steadily better in our configuration, while it has siginificantly greater complexity.

>>>>

Multiple-input-multiple-output (MIMO) is the future of wireless communication, but the large number of antennae makes it difficult to estimate its channel state information.
Since millimeter wave (mm-Wave) band, which is often used together with MIMO, is known to exhibit sparsity, results on compressive sensing suggest that, on mm-Wave band, fewer channel measurements shall suffice.
Current literature prefers orthogonal matching pursuit (OMP) due to its lower complexity.
It is interesting to note that Dantzig Selector (DS), claimed to have various performance guarantee, has seldom been examined.

In this treatise, we consider a mm-Wave MIMO channel, and a hybrid beamforming structure at both the transmitter and receiver end.
We demonstrate that DS can be applied on a entrywise i.i.d.\ random beamformers, and give a bound for its expected error norm, which holds for high probability.
DS is cast as a linear program, and simulation is done, showing that, in our problem setting, DS is superior in terms of relative error norm.

### 2020-12-31 treatise-pdflatex/notation.tex
Create pdflatex version

\starttable[|l|l|l|] \HL
\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
\NC \m {\RB {1+3} \RB {2+4}} \VL round parentheses \VL used for precedence \AR \HL
\NC \m {f \SB {x}} \VL square brackets \VL used for arguments or parameter \AR \HL
\NC \m {\CB {2, 3, 5, 7}} \VL curly braces \VL used for sets \AR \HL
\NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
\NC \m {\MF {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
\NC \m {\MF {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
\NC \m {\V {a}} \VL vector \VL \AR \HL
\NC \m {\M {A}} \VL matrix \VL \AR \HL
\NC \m {\V {1}} \VL all-1 vector \VL dimension will be specified \AR \HL
\NC \m {\V {0}} \VL all-0 vector \VL dimension will be specified \AR \HL
\NC \m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL
\NC \m {\M {A} _{\SB {m,n}}} \VL \m {m,n}-th entry of \m {\M {A}} \VL \AR \HL
\NC \m {\V {a} _{\SB {0}}} \VL the first component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
\NC \m {\MB {K}} \VL either \m {\MB {R}} or \m {\MB {C}} \VL  \AR \HL
\NC \m {\MB {K} ^{N}} \VL Hilbert space \m {\MB {K}^N} over \m {\MB {K}} \VL  \AR \HL
\NC \m {\MB {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
\NC \m {m\; \Rm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \Rm {Mod}\; n <n} \AR \HL
\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
\NC \m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
\NC  \VL component of \m {\V {a}} \VL  \AR \HL
\NC \m {\MB {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
\NC \m {\MB {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
\NC \m {\Ss {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
\stoptable

>>>>

\starttable[|l|l|l|] \HL
\NC Expression \VL Meaning or Definition \VL More Explanation \SR \HL
\NC \m {\Nm {a}} \VL magnitude \VL for real or complex numbers \AR \HL
\NC \m {\mathfrak {Re} \SB {a}} \VL real part \VL for complex numbers \AR \HL
\NC \m {\mathfrak {Im} \SB {a}} \VL imaginary part \VL for complex numbers \AR \HL
\NC \m {\V {a}} \VL vector \VL \AR \HL
\NC \m {\M {A}} \VL matrix \VL \AR \HL
\NC \m {\V {1}} \VL all-1 vector \VL dimension will be specified \AR \HL
\NC \m {\V {0}} \VL all-0 vector \VL dimension will be specified \AR \HL
\NC \m {\V {a} _{\SB {n}}} \VL \m {n}-th component of \m {\V {a}} \VL \AR \HL
\NC \m {\M {A} _{\SB {m,n}}} \VL \m {m,n}-th entry of \m {\M {A}} \VL \AR \HL
\NC \m {\V {a} _{\SB {0}}} \VL the first component of \m {\V {a}} \VL  \AR \HL
\NC \m {\M {A} _{\SB {0,0}}} \VL the upper-left entry of \m {\V {A}} \VL  \AR \HL
\NC \m {\mathbb {K}} \VL either \m {\mathbb {R}} or \m {\mathbb {C}} \VL  \AR \HL
\NC \m {\mathbb {K} ^{N}} \VL Hilbert space \m {\mathbb {K}^N} over \m {\mathbb {K}} \VL  \AR \HL
\NC \m {\mathbb {K} ^{M \D N}} \VL collection of \m {M} by \m {N} matrices \VL  \AR \HL
\NC \m {m\; \mathrm {Mod}\; n} \VL remainder of \m {m} divided by \m {n} \VL with \m {m, n \geq 0} and \m {0 \leq m\; \mathrm {Mod}\; n <n} \AR \HL
\NC \m {\VNm {\V {a}} _p} \VL \m {\ell_p}-norm of \m {\V {a}} \VL \m {p >0} \AR \HL
\NC \m {\VNm {\V {a}} _\infty} \VL the maximum-magnitude \VL  \AR
\NC  \VL component of \m {\V {a}} \VL  \AR \HL
\NC \m {\mathbb {P} \SB {A}} \VL probability of event \m {A} \VL  \AR \HL
\NC \m {\mathbb {E} \SB {X}} \VL expectation of random variable \m {X} \VL  \AR \HL
\NC \m {\mathsf {Var} \SB {X}} \VL variance of random variable \m {X} \VL  \AR \HL
\stoptable
